BIP-Predictor

### 2025-05-14 Sweave/BIP_predictor.Rnw
Update BIP_predictor.Rnw

#----------------      
# B. Direct forecasts
# -The main difference to M-SSA above is the specification of the explanatory variables in the data 
#     matrix dat: we here use x_mat instead of mssa_array. 
#   -We select all indicators (one could easily change this setting but results are only marginally effected as long as ifo and ESi are included)
#   -Note that the data matrix here does not depend on j, in contrast  to the M-SSA components above    
      dat<-cbind(c(x_mat[(shift+lag_vec[1]+1):nrow(x_mat),1],rep(NA,shift+lag_vec[1])),x_mat[,sel_vec_direct_forecast])
      rownames(dat)<-rownames(x_mat)
# Two variants for data set:  
      if (T)
      {
# 1. Same sample as M-SSA (due to filter initialization the first L observations are lost) 
        dat<-dat[L:nrow(dat),]
# Same length as M-SSA      
        nrow(na.exclude(dat))
      } else
      {
# 2. Full data, including the first L observations (makes sense since the data is available) 
        dat<-dat[1:nrow(dat),]
      }
      perf_obj<-optimal_weight_predictor_func(dat,in_out_separator,use_garch,shift,lag_vec,align_sample,reg_type,lambda_reg)
# Retrieve out-of-sample performances: p-values and forecast MSE, with/without Pandemic 
      p_mat_direct[shift+1,k]<-perf_obj$p_value 
      p_mat_direct_without_covid[shift+1,k]<-perf_obj$p_value_without_covid 
      MSE_oos_direct<-perf_obj$MSE_oos
      MSE_oos_direct_without_covid<-perf_obj$MSE_oos_without_covid

>>>>

#----------------      
# B. Direct forecasts
# -The main difference to M-SSA above is the specification of the explanatory variables in the data 
#     matrix dat: we here use x_mat instead of mssa_array. 
#   -We select all indicators (one could easily change this setting but results are only marginally effected as long as ifo and ESi are included)
#   -Note that the data matrix here does not depend on j, in contrast  to the M-SSA components above    
      dat<-cbind(c(x_mat[(shift+lag_vec[1]+1):nrow(x_mat),1],rep(NA,shift+lag_vec[1])),x_mat[,sel_vec_direct_forecast])
      rownames(dat)<-rownames(x_mat)
# Two variants for data set:  
      if (align_sample)
      {
# 1. Same sample as M-SSA (due to filter initialization the first L observations are lost) 
        dat<-dat[L:nrow(dat),]
# Same length as M-SSA      
        nrow(na.exclude(dat))
      } else
      {
# 2. Full data, including the first L observations (makes sense since the data is available) 
        dat<-dat[1:nrow(dat),]
      }
      perf_obj<-optimal_weight_predictor_func(dat,in_out_separator,use_garch,shift,lag_vec,align_sample,reg_type,lambda_reg)
# Retrieve out-of-sample performances: p-values and forecast MSE, with/without Pandemic 
      p_mat_direct[shift+1,k]<-perf_obj$p_value 
      p_mat_direct_without_covid[shift+1,k]<-perf_obj$p_value_without_covid 
      MSE_oos_direct<-perf_obj$MSE_oos
      MSE_oos_direct_without_covid<-perf_obj$MSE_oos_without_covid
